A Traveling Salesman Solution For The Capitals of All African Nations

### 2009-10-31 paper/paper.tex
added spelling check
stuff

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{mdwlist}

@@

\section{Programs}
A much longer  example was written by Gil

@@

@@

\section{Analysis}

\end{document}

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{mdwlist}
\usepackage{amssymb,amsmath}
\usepackage{cite}
\usepackage[bookmarks=false,colorlinks=true,linkcolor={blue},pdfstartview={XYZ null null 1.22}]{hyperref} 
\usepackage{url}

@@

\section{Programs}

The TSP was solved using the Python 2.6 programming language.

I leveraged software written by John Montgomery \cite{cite_key2}

The results were then visualized using Google maps mapping API.

Two methods were

@@

\begin{align}
  yDis = ( lat2 - lat1 ) * Nautical Miles Per Latitude\\
  xDis = ( \cos( lat1 - \frac{\pi}{180} ) + \cos( lat2 - \frac{\pi}{180} ) ) * ( lon2 - lon1 ) * \frac{Nautical Miles Per Longitude}{2}\\
  tDistance = \sqrt{ yDis^{2} + xDis^{2} } * Miles per Nautical Miles\\
\end{align}

@@

\section{Analysis}
\begin{thebibliography}{99}
\bibitem{cite_key1} Montgomery, John {\it Tackling The Travelling Salesman Problem}{\href{http://www.psychicorigami.com/category/tsp/}{ http://www.psychicorigami.com/category/tsp/} }, {\bf 2007}
\bibitem{cite_key2} Mead, C. A.; Truhlar, D. G. {\it J. Chem. Phys.} {\bf 1983}, {\it 78}, 6344.
\end{thebibliography}
\end{document}
